### 2021-02-01 experiments.tex
fse format
version info for solidity

We analyzed three well-known tools for static analysis of Solidity smart contracts: Slither \cite{slither}, SmartCheck \cite{smartcheck}, and Securify \cite{Securify}.  Slither, based on an SSA-based intermediate language (SlithIR \cite{slither}) is an open-source tool from Trail of Bits.  SmartCheck, developed by SmartDec, translates Solidity source directly to an XML-based representation, then uses \emph{XPath} patterns to define problems.  Securify, from SRI Systems Lab at ETH Zurich, works at the bytecode level, first parsing and decompiling contracts, then translating to \emph{semantic facts} in order to look for problems.

@@

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & \multicolumn{2}{|c|}{Findings} & \multicolumn{2}{|c|}{Mutation Score}  & Mutant \\
    Tool & Mean & Median & Mean & Median & Ratio\\
    \hline
    \hline
    Pylint & 2.24 & 1.00 & 0.22 & 0.20 & 0.097 \\
    Clean (0) & - & - & - & - & - \\
    \hline
    pyflakes & 2.4 & 1.00 & 0.03 & 0.00 & 0.012 \\
    Clean (12) & - & - & 0.02 & 0.00 & - \\
    \hline
    PyChecker & 0.56& 0.00 & 0.10 & 0.00 &  0.183 \\
    Clean (21) & - & - & 0.01 & 0.00 \\
    \hline
  \end{tabular}
  \caption{Python tool results over all projects.}
  \label{tab:scorepython}
\end{table}

>>>>

We analyzed three well-known tools for static analysis of Solidity smart contracts: Slither \cite{slither}\footnote{pip version 0.6.1}), SmartCheck \cite{smartcheck}\footnote{github commit 17fb98d9759eebeca1f92d48be52b85a1f5d8b89}, and Securify \cite{Securify}\footnote{github commit 0ffde61b9527be70b147d3ab687f11993d99212b}.  Slither, based on an SSA-based intermediate language (SlithIR \cite{slither}) is an open-source tool from Trail of Bits.  SmartCheck, developed by SmartDec, translates Solidity source directly to an XML-based representation, then uses \emph{XPath} patterns to define problems.  Securify, from SRI Systems Lab at ETH Zurich, works at the bytecode level, first parsing and decompiling contracts, then translating to \emph{semantic facts} in order to look for problems.

@@

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & \multicolumn{2}{|c|}{Findings} & \multicolumn{2}{|c|}{Mutation Score}  & Mutant \\
    Tool & Mean & Median & Mean & Median & Ratio\\
    \hline
    \hline
    Pylint & 2.24 & 1.00 & 0.22 & 0.20 & 0.097 \\
    Clean (0) & - & - & - & - & - \\
    \hline
    pyflakes & 2.4 & 1.00 & 0.03 & 0.00 & 0.012 \\
    Clean (12) & - & - & 0.02 & 0.00 & - \\
    \hline
    PyChecker & 0.56& 0.00 & 0.10 & 0.00 &  0.183 \\
    Clean (21) & - & - & 0.01 & 0.00 \\
    \hline
  \end{tabular}
  \caption{Python tool results over all projects (old).}
  \label{tab:scorepython}
\end{table}

\begin{table}
  \begin{tabular}{l|r|r|r|r|r}
    & \multicolumn{2}{|c|}{Findings} & \multicolumn{2}{|c|}{Mutation Score}  & Mutant \\
    Tool & Mean & Median & Mean & Median & Ratio\\
    \hline
    \hline
    Pylint & 11.87 & 4.00 & 0.20 & 0.19 & 0.02 \\
    Clean (3) & - & - & 0.09 & 0.11 & - \\
    \hline
    pyflakes & 1.52 & 0.00 & 0.08 & 0.06 & 0.05 \\
    Clean (15) & - & - & 0.09 & 0.08 & - \\
    \hline
    MyPy & 3.00 & 3.00 & 0.05 & 0.03 &  0.02 \\
    Clean (3) & - & - & 0.03 & 0.01 & - \\
    \hline
  \end{tabular}
  \caption{Python tool results over all projects (new).}
  \label{tab:scorepython}
\end{table}
